---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Binomial

##Overview: 

The _Binomial_ pacakge provides functions to calculate and visualize binomial distirbutions.

A binomial distritbution can be generated with: 

* _n_ trials 
* _p_ probability

Basic summary functions calculate statistics of a generated binomial distribution:

* `bin_mean(trials,probability)` 
* `bin_variance(n,p)`
* `bin_mode(n,p)`
* `bin_skewness(n,p)`
* `bin_kurtosis(n,p)`

More complex summary funtions calculate the binomial distribution and the probability of successes:

* `bin_variable(trials,probability)`
* `bin_choose(trials,successes)`
* `bin_probability(success,trials,probability)`
* `bin_distribution(trials,probability)`
* `bin_cumulative(trials,probability)`

To learn about these functions, read the vignette provided or call `?bin_variable`.

##Installation:

Install the development version from GitHub via the package `"devtools"`:

```r
# Load helper detools:
install.packages("devtools") 
# To load Binomial (without vignettes):
devtools::install_github("Dyang11/binomial")
```

To learn about the functions, install Binomail with vignettes:

```r
devtools::install_github("Dyang11/binomial", build_vignettes = TRUE)
```

##Usage:

Let us supposed we are simulating 10 coin tosses, where a "success" is a heads flip. 

```{r message=FALSE,warning = FALSE}
library(Binomial)

#Set variable amounts
trials <- 10
probability <- 0.5

bin_mean(trials,probability)

bin_variable(trials,probability)

summary(bin_variable(trials,probability))

bin_distribution(trials,probability)

plot(bin_distribution(trials,probability))

bin_cumulative(trials,probability)

plot(bin_cumulative(trials,probability))
```

---
Created by Daniel Yang for Stat 133, Spring 2019. 05/03/19
