---
title: "Binomial Tutorial"
author: "Daniel Yang"
date: "5/1/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Binomial_tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(Binomial)
```

#Introduction: 

This document is an introduction to the __Binomial__ package. The binomial package is a implementation of basical statistical functions; the methods are designed to calculate and visualize binomial distributions.

#Binomial Basics

Let's consider a case with _10_ trials, with each trial having a  _0.7_ chance of succeededing.

##Basic Statistical Measures 

Included in the package are 5 base summary functions: 

* Mean 
* Variance 
* Mode 
* Skewness
* Kurtosis

Let's review each one more carefully.

###Bin_Mean

The binomial mean is the average number of successes in _n_ trials given _p_ probability of success. To get the mean, call `bin_mean(trials, probability)`

```{r}
bin_mean(10,0.7)
```

###Bin_Variance

The binomial variance is the square of the standard deviation of a binomial distribution. To get the variance, call `bin_variance(trials, probability)`

```{r}
bin_variance(10,0.7)
```

###Bin_Mode

The binomial mode is the most likely number of succeses. To obtain the mode, call `bin_mode(trials,probability)`

```{r}
bin_mode(10,0.7)
```

###Bin_Skewness

The binomial skewness is a measure of the asymmetry of the binomial distribution. To obtain the skewness, call `bin_skewness(trials,probability)`

```{r}
bin_skewness(10,0.7)
```

###Bin_Kurtosis

The binomial kurtosis is a measure of the sharpness of a peak in a frequency-distirbution curve. To obtain the kurtosis, call `bin_kurtosis(trials,probability)`

```{r}
bin_kurtosis(10,0.7)
```

###Summarize all variables with bin_variable

`bin_variable(trials,probability)` provides a basic return

```{r}
bin_variable(10,0.7)
```

To easily obtain a summary of all the above binomial variables, use `summary(bin_variable(trials,probability))`

```{r}
summary(bin_variable(10,0.7))
```

##Binomial Distribution Calculations

The following main functions are to calculate binomial distributions. Two methods are used to calculate some more basic statistics: 

* bin_choose
* bin_probability

These functions can be used to model coin flips, for example.

###Bin_choose

`bin_choose(trials, successes)` provides the number of permutations to obtain the specific number of successes in the given amount of trials.

```{r}
bin_choose(10,6)
#This means there are 210 different ways to obtain 6 successes in 10 trials
```
###Bin_probability

`bin_probability(successes,trials,probability)` provides the percent chance of obtaining _k_ successes in _n_ trials with a _p_ probability of succeeding on each trial. This function can be used to determine how likely it is to get 1, 2, or 3 heads for 5 total coin flips.

```{r}
bin_probability(6,10,0.6)
#This means there is a around a 25% chance of obtaining 6 successes in 10 trials where each trial has a 60% chance of succeeding.

bin_probability(1:3,5,0.5)
#Calling bin_probability with multiple success values gives us the seperate probability of obtaining each success value. There is about a 15% chance of obtaining 1 success and about the same 31% chance of obtaining 2 or 3 successes out of 5. 

```
##Binomial Distribution Visualization

Finally, the two following functions provide a visualization method for binomial distributions.

* bin_distribution
* bin_cumulative
 
###Visualize likelihood distributions with bin_distribution and bin_cumulative

`bin_distirbution(trials,probability)` returns a data frame with how likely it is to obtiain each possible success number in _n_ trials.

```{r}
#This function call provides the likelihood of seeing 0, 1, 2, 3, or 4 heads in 4 coin tosses.

bin_distribution(4,0.5)
```
An easier way to see this data is with a frequency histogram, which can be obtaining by calling `plot(bin_distribution(trials,probability))`

```{r}
plot(bin_distribution(4,0.5))
#Here, we see that flipping 2 heads is the most likely option in 4 coin tosses.
```

`bin_cumulative(trials,probability)` provides additional information about the cumulative probability 

```{r}
#This function call provides the likelihood of seeing 0, 1, 2, 3, or 4 heads in 4 coin tosses, along with the cumulative probability.

bin_cumulative(4,0.5)
```

Finally, the cumulative probability can be visualized by `plot(bin_cumulative(trials,probability))`

```{R}
plot(bin_cumulative(10,0.5))
#We see that most iterations of 10 coin flips will have less than 8 "heads"; the cumulative probability that we get less than 8 heads is above 90%
```

